\chapter*{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begin{enumerate}[label=\arabic*)\hspace{1em}, leftmargin=1cm, itemsep=0em]
	\item Jain K., Adapa K.S., Grover K., Sarvadevabhatla R.K., Purini S. A Cloud-Fog Architecture for Video Analytics on Large Scale Camera Networks Using Semantic Scene Analysis // 2023 IEEE/ACM 23rd International Symposium on Cluster, Cloud and Internet Computing (CCGrid). — 2023. — P. 513–523. DOI: 10.1109/CCGrid57682.2023.00054.
	\item Prometheus monitoring system and time series database. — URL: https://prometheus.io/docs/ (дата обращения: 05.06.2025).
	\item Grafana: The open observability platform. — URL: https://grafana.com/docs/ (дата обращения: 05.06.2025).
	\item Apache Kafka: A distributed streaming platform. — URL: https://kafka.apache.org/documentation/ (дата обращения: 05.06.2025).
	\item Docker: Accelerated Container Application Development. — URL: https://docs.docker.com/ (дата обращения: 05.06.2025).
	\item Renault A., Bondu A., Lemaire V., Gay D. Automatic Feature Engineering for Time Series Classification: Evaluation and Discussion // 2023 International Joint Conference on Neural Networks (IJCNN). — 2023. — P. 1–10. DOI: 10.1109/IJCNN54540.2023.10191074.
	\item Box G.E.P., Jenkins G.M. Time Series Analysis: Forecasting and Control. — San Francisco: Holden-Day, 1970.
	\item Prokhorenkova L., Gusev G., Vorobev A., Dorogush A.V., Gulin A. CatBoost: unbiased boosting with categorical features // arXiv preprint arXiv:1706.09516. — 2019. — URL: https://arxiv.org/abs/1706.09516 (дата обращения: 05.06.2025).
	\item Hochreiter S., Schmidhuber J. Long Short-Term Memory: Technical Report FKI-207-95. — Munich: Fakultät für Informatik, Technische Universität München, 1995.
	\item Time-Series-Library: A Library for Advanced Deep Time Series Models. — URL: https://github.com/thuml/Time-Series-Library (дата обращения: 05.06.2025).
	\item AutoTS: Automated Time Series Forecasting. — URL: https://github.com/winedarksea/AutoTS (дата обращения: 05.06.2025).
	\item Deploying a Scalable Object Detection Inference Pipeline, Part 1. — URL: https://developer.nvidia.com/blog/deploying-a-scalable-object-detection-inference-pipeline/ (дата обращения: 05.06.2025).
	\item Deploying a Scalable Object Detection Pipeline: The Inferencing Process, Part 2. — URL: https://developer.nvidia.com/blog/deploying-a-scalable-object-detection-pipeline-the-inferencing-process-part-2/ (дата обращения: 05.06.2025).
	\item Latency in End-to-End IP Monitoring: Why It Matters and What to Know. — URL: https://tagvs.com/blog/latency-in-end-to-end-ip-monitoring-why-it-matters-and-what-to-know/ (дата обращения: 05.06.2025).
	\item Beyond Monitoring: The Power of Observability. — URL: https://www.onec1.com/blog/beyond-monitoring-the-power-of-observability/ (дата обращения: 05.06.2025).
	\item Sassu A., Pili R., Marrocu M., Faticanti F. Deep-Framework: A Distributed, Scalable, and Edge-Oriented Framework for Real-Time Analysis of Video Streams // Sensors. — 2021. — Vol. 21, № 12. — P. 4045. DOI: 10.3390/s21124045.
	\item Aloorravi S. Mastering Time Series Analysis and Forecasting with Python. — Orange Education Pvt Ltd, 2024.
	\item Boniol P., Liu Q., Huang M., Palpanas T., Paparrizos J. Dive into Time-Series Anomaly Detection: A Decade Review // arXiv preprint arXiv:2412.20512. — 2024. — URL: https://arxiv.org/abs/2412.20512 (дата обращения: 05.06.2025).
	\item Jiang Y., Ning K., Pan Z. et al. Multi-modal Time Series Analysis: A Tutorial and Survey // arXiv preprint arXiv:2503.13709. — 2025. — URL: https://arxiv.org/abs/2503.13709 (дата обращения: 05.06.2025).
	\item Oreshkin B.N., Carpov D., Chapados N., Bengio Y. N-BEATS: Neural basis expansion analysis for interpretable time series forecasting // arXiv preprint arXiv:1905.10437. — 2020. — URL: https://arxiv.org/abs/1905.10437 (дата обращения: 05.06.2025).
\end{enumerate}